%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Product Desgin, Software Engineer} % Job title
    {\href{https://indexpeople.nl}{Index People} (indexpeople.nl)} % Organization
    {Haarlem, The Netherlands} % Location
    {Nov. 2018 - Mar. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {
        Implementation of the customer and admin portal of Index People and automating\\ all the processes within the company
        }
      \item {Creating bi-directional connection between Salesforce and the portal}
      \item {Product design and architecture}
      \end{cvitems}
	}
%---------------------------------------------------------
  \cventry
    {Co-founder, Software Engineer} % Job title
    {\href{https://www.xecolabs.com}{Xeco Labs} (xecolabs.com)} % Organization
    {Amsterdam, The Netherlands} % Location
    {Nov. 2017 - PRESENT} % Date(s)
    {
      \begin{cvitems} 
      \item {Full stack software development for different projects.}
      \item {Blokker Blokjes: Blokker loyalty program to offer stocks to the customers in exchanges for loyalty points.}
      \item {Index People Portal: Implementation of the customer and admin portal of Index People and automating\\ all the processes within the company}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Creator} % Job title
    {\href{https://www.coinograph.io}{Coinograph} (coinograph.io)} % Organization
    {Amsterdam, The Netherlands} % Location
    {Nov. 2017 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Coinograph is a crypto market data provider which collects and offers crypto market data from different exchanges}
      \item {Developed Coinograph bot and backend services.}
      \item {Autmoated provisioning	and deployment of services using Ansible.}
      \item {Set up CI/CD using Jenkins.}	
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Mentor} % Job title
    {\href{https://www.hackyourfuture.net}{Hack Your Future}} % Organization
    {Amsterdam, The Netherlands} % Location
    {Sep. 2017 - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Teacher and mentor helping refugees learn programming and develop their career.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {CTO} % Job title
    {\href{https://www.jump.work/}{Jump.Work}} % Organization
    {Amsterdam, The Netherlands} % Location
    {Feb. 2016 - Jul. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for the entire product stack of the company based on Python/Django, Postgresql, Heroku, Redis (Backend) and React/Redux and Nodejs (Frontend).}
        \item {Design and architecture of the whole tech stack (FE and BE)}
        \item {Implementation of the backend.}
        \item {Implementation of several distributed web scrapers to collect required information.}
        \item {Implementation of a suit of phsychometric tests to assess candindates on Jump.Work platform.}
        \item {Working with the business/design team to translate the work into actionable sprints.}
        \item {A/B testing features.}
        \item {Training junior developers.}
        \item {Working with external stakeholders on technical challenges and finding solutions.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelance Software Engineer} % Job title
    {\href{https://www.gingerpayments.com}{Ginger Payments}} % Organization
    {Amsterdam, The Netherlands} % Location
    {Jul. 2015 - Jan. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Development of credit card payment for Kassa Compleet and integration of Equens workflows.}
      \item {Major refactoring to renew the backend and improve the code quality.}
      \item {Coordination with external companies on product development.}
      \item {Recruitment of new software developers.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {\href{https://www.tmg.nl/nl}{Telegraaf Media Groep}} % Organization
    {Amsterdam, The Netherlands} % Location
    {Aug. 2013 - Jun. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Redesign and implementation of Telegraaf Android application.}
        \item {Backend and Android development for Telesport application.}
        \item {Implementation, optimisation and scaling of Oranjepoul website for 2014 World Cup predictions.}
        \item {Contribution to the hiring process by evaluating job applications and conducting interviews.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {West Consulting B.V.} % Organization
    {Delft, The Netherlands} % Location
    {Jul. 2012 - Jul. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implenetation of reporting and visualisation of Rijkswaterstaat Interaction Monitor to get reports on highway activities.}
        \item {Android development for bridge game uBid.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Vembler} % Organization
    {Amsterdam, The Netherlands} % Location
    {Sep. 2012 - May. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design and development of Vembler online product (tech stack Python/Django).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Beonten, Inc.} % Organization
    {Amsterdam, The Netherlands \& Boston, USA} % Location
    {Sep. 2011 - Jan. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Remote contribution to Barter product development.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
